Group Theory in Physics (Course Note)

### 2016-09-27 Complex Geometry - index/misc/complex geometry-misc.tex
Yesterday's note for class about group theory. And new complex geometry notes.

        \subsubsection{Why \texorpdfstring{
                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
                }{}(continued)
            }
        With above theorem, the proof of equation 
        \ref{eq:sec.1.1.2_why_glnc_injectInto_positive_comp} 
        is straight forward. Since for 
        $(a_{ij})= A\in \mathrm{GL}(n,\mathbb{C})$, it injects into
        $\mathrm{GL}(2n,\mathbb{R})$ as matrices of the form:
        \begin{align*}
            \left( \begin{array}{ccc}
             \text{...} & \text{...} & \text{...} \\
             \text{...} & H a_{\text{ij}} & \text{...} \\
             \text{...} & \text{...} & \text{...} \\
            \end{array} \right)
        \end{align*}
        where:
        \begin{align*}
            H(z\equiv x+iy)=\left( \begin{array}{cc}
                    x & -y \\
                    y & x \\
            \end{array}\right)
        \end{align*}
        Since $H(a_{ij})$ commutes with each other (proved by calculation),
        we can use the theorem in previous part to show that:
        \begin{align*}
            \mathrm{det_\mathbb{R}}(A) =
            \mathrm{det_\mathbb{R}}  (\mathrm{det_\mathbb{C}}(A))
            = |\mathrm{det_\mathbb{C}}(A) |^2 \geq 0
        \end{align*}
        Notice that I have been sloopy in language, but the meaning should
        be clear.

@@

    \subsection{Lifting Property}
    \label{sec:Lifting-Property}
    \paragraph{Lift of morphisms}
    \begin{defi}[Lift of morphisms]
    \nomenclature{Lift of morphisms}{\nomrefpage.}
        The \textbf{lift} of a morphism $f: Y\to B$ along an epimorphism
        \footnote{Epimorphism is the category analogy of surjective
        functions in set theory}. (or more general map) $p:X\to B$ is a
        morphism $\tilde{f}: Y\to X$ such that $f = p\circ\tilde{f}$.
    \end{defi}
    $$
    \xymatrix{
        X\ar[r]^p                    & B \\
        Y\ar[ur]^f\ar[u]^{\tilde{f}} & \\
    }
    $$
    \begin{defi}[Lift property]
    \nomenclature{Lift property}{\nomrefpage.}
        We say that $f$ has a \textbf{left lifting property} w.r.t $g$, or
        equivalently that $g$ has a \textbf{right lifting property} w.r.t
        $f$, if and only if for every commutative diagram below:
        $$
        \xymatrix{
        a\ar[r]^u\ar[d]^f & c\ar[d]^g \\
        b\ar[r]^v         & d
        }
        $$
        there is an arrow $\gamma$, s.t. both triangles in the followinng
        diagram commutes.
        $$ \xymatrix{
        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
        b\ar[r]^v\ar[ru]^{\gamma} & d
        }$$
        Such an arrow $\gamma$ is called a \textbf{lift} or a 
        \textbf{solution} to the lifting problem $(u,v)$.
        If such $\gamma$ is unique, i.e. we have:
        $$ \xymatrix{
        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
        b\ar[r]^v\ar@{.>}[ru]^{\gamma} & d
        }$$
        Then we say $f$ is \textbf{orthogonal} to $g$, denoted $f \perp g$.
    \end{defi}
    ref \cite{nlab-lift}.

    % Resources: https://ncatlab.org/nlab/show/fibration
    %            https://ncatlab.org/nlab/show/homotopy+lifting+property
    %            https://en.wikipedia.org/wiki/Homotopy_lifting_property
    %            https://en.wikipedia.org/wiki/Fibration
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
  \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
  \bibitem{math.se_4} \href{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
  {Similar matrices and field extensions}
  \bibitem{math.se_set-of-almost} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}
  \bibitem{nlab-lift}\href{https://ncatlab.org/nlab/show/lift}{nLab Lift}
\end{thebibliography}
\printnomenclature

>>>>

        \subsubsection{Why \texorpdfstring{
                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
                }{}(continued)
            }
        With above theorem, the proof of equation 
        \ref{eq:sec.1.1.2_why_glnc_injectInto_positive_comp} 
        is straight forward. Since for 
        $(a_{ij})= A\in \mathrm{GL}(n,\mathbb{C})$, it injects into
        $\mathrm{GL}(2n,\mathbb{R})$ as matrices of the form:
        \begin{align*}
            \left( \begin{array}{ccc}
             \text{...} & \text{...} & \text{...} \\
             \text{...} & H a_{\text{ij}} & \text{...} \\
             \text{...} & \text{...} & \text{...} \\
            \end{array} \right)
        \end{align*}
        where:
        \begin{align*}
            H(z\equiv x+iy)=\left( \begin{array}{cc}
                    x & -y \\
                    y & x \\
            \end{array}\right)
        \end{align*}
        Since $H(a_{ij})$ commutes with each other (proved by calculation),
        we can use the theorem in previous part to show that:
        \begin{align*}
            \mathrm{det_\mathbb{R}}(A) =
            \mathrm{det_\mathbb{R}}  (\mathrm{det_\mathbb{C}}(A))
            = \mathrm{det}_\mathbb{R}(aI+bJ)
            =\mathrm{det}\left(\begin{array}{cc}
                    a & -b\\
                    b & a\\
            \end{array}\right) \geq 0
        \end{align*}
        Notice that I have been sloopy in language, but the meaning should
        be clear.

@@

    \subsection{Fibration}
    \label{sec:Fibration}
    \paragraph{Lift of morphisms}
    \begin{defi}[Lift of morphisms]
    \nomenclature{Lift of morphisms}{\nomrefpage.}
        The \textbf{lift} of a morphism $f: Y\to B$ along an epimorphism
        \footnote{Epimorphism is the category analogy of surjective
        functions in set theory}. (or more general map) $p:X\to B$ is a
        morphism $\tilde{f}: Y\to X$ such that $f = p\circ\tilde{f}$.
    \end{defi}
    $$
    \xymatrix{
        X\ar[r]^p                    & B \\
        Y\ar[ur]^f\ar[u]^{\tilde{f}} & \\
    }
    $$
    \begin{defi}[Lift property]
    \nomenclature{Lift property}{\nomrefpage.}
        We say that $f$ has a \textbf{left lifting property} w.r.t $g$, or
        equivalently that $g$ has a \textbf{right lifting property} w.r.t
        $f$, if and only if for every commutative diagram below:
        $$
        \xymatrix{
        a\ar[r]^u\ar[d]^f & c\ar[d]^g \\
        b\ar[r]^v         & d
        }
        $$
        there is an arrow $\gamma$, s.t. both triangles in the followinng
        diagram commutes.
        $$ \xymatrix{
        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
        b\ar[r]^v\ar[ru]^{\gamma} & d
        }$$
        Such an arrow $\gamma$ is called a \textbf{lift} or a 
        \textbf{solution} to the lifting problem $(u,v)$.
        If such $\gamma$ is unique, i.e. we have:
        $$ \xymatrix{
        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
        b\ar[r]^v\ar@{.>}[ru]^{\gamma} & d
        }$$
        Then we say $f$ is \textbf{orthogonal} to $g$, denoted $f \perp g$.
    \end{defi}
    ref \cite{nlab-lift}.

    \begin{defi}[Homotopy lifting property]
    \nomenclature{Homotopy lifting property}{\nomrefpage.}
    Let $C$ be a category with \textbf{products} and with \textbf{interval
    object} $I$. A morphism $E\to B$ has the homotopy lifting property if it
    has the right lifting property w.r.t all morphisms of the form
    $(\text{Id},0):Y \to Y\times I$.
    \end{defi}
    $$ \xymatrix{
        Y\ar[r]^f\ar[d]                 & E\ar[d]^p \\
        Y\times I\ar[r]^F\ar[ru]^\sigma & B
    }$$
    Note: the term \textbf{products} and \textbf{interval object} mentioned
    above are category analogy of cartisian products and unit interval $[0,1]$
    in our daily mathematics. Since I will be concentrated in the case of a
    topological space, I will simply regard them just as topological products
    and the unit interval.

    \paragraph{Fibrations}
    \begin{defi}[Hurewicz fibration]
    \nomenclature{Hurewicz fibration}{\nomrefpage.}
        A map $p$ is called a Hurewicz fibration if it satisfies the homotopy
        lifting property w.r.t to all spaces $X$.
    \end{defi}
    \begin{defi}[Serre fibration]
    \nomenclature{Serre fibration}{\nomrefpage.}
        A map $p$ is called a Serre fibration if it satisfies the homotopy
        lifting property w.r.t to all discs $X$.
    \end{defi}
    Notes: by discs, I think he means closed discs, or closed balls, because he
    also mentioned "equivalently" closed cubes.

    Ref \cite{nlab-homotopy-lifting-property}.
    % Resources: https://ncatlab.org/nlab/show/fibration
    %            https://ncatlab.org/nlab/show/homotopy+lifting+property
    %            https://en.wikipedia.org/wiki/Homotopy_lifting_property
    %            https://en.wikipedia.org/wiki/Fibration
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
    \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
    \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
    \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
    \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
    \bibitem{math.se_4} \href{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
      {Similar matrices and field extensions}
    \bibitem{math.se_set-of-almost} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}
    \bibitem{nlab-lift}\href{https://ncatlab.org/nlab/show/lift}{nLab Lift}
    \bibitem{nlab-homotopy-lifting-property}\href{https://ncatlab.org/nlab/show/homotopy+lifting+property}{nLab Homotopy lifting property}, \href{https://ncatlab.org/nlab/show/cartesian+product}{nLab Cartesian product}, \href{https://ncatlab.org/nlab/show/interval+object}{nLab Interval object}.
\end{thebibliography}
\printnomenclature

### 2016-09-27 Group Theory in Physics/group theory in physics.tex
New notes about adjoint operator of antilinear operators.
1. Begin really tackling the first problem in Complex Geometry. 2. Editing some green function code. 3. New course notes about Advanced Quantum Mechanics.
Yesterday's note for class about group theory. And new complex geometry notes.

After mentioning the Poinc\'{a}re group, he produces to review some
concepts about linear algebra:
\begin{enumerate}
    \item The axioms of linear space, using quantum mechanics
        as basic example (Omitted).
    \item Some common concepts of linear space: linear-independence,
        subspace, direct sum, linear operators, its matrix representation. (Omitted)
    \item Introducing the complete antisymmetric tensor 
        $\epsilon^{a_1,\cdots,a_n}$. Some properties:
        \begin{align}
            \frac{1}{(m-n)!} \sum_{a_{n+1},\cdots, a_m}
            & \epsilon_{a_1,\cdots,a_n,a_{n+1},a_m}
            \epsilon_{b_1,\cdots,b_n,a_{n+1},a_m}\nonumber
            \\
            &= \sum_{p_1,\cdots,p_n} 
            \epsilon_{p_1,\cdots,p_n} 
                \delta_{a_1,b_{p_1}}\cdots \delta_{a_n,b_{p_n}}
                \\
            \epsilon_{ab}\epsilon_{rs} &=
                \delta_{ar}\delta_{bs}-\delta_{as}\delta_{br}
                \\
            \sum_d\epsilon_{abd}\epsilon_{rsd} &=
                \delta_{ar}\delta_{bs} + \delta_{as}\delta_{br}
        \end{align}
    \item Some special matrices.
    \item Fact: If $R\Gamma = \Gamma R$, and 
        $\Gamma$ is diagonal. (let $\mu\neq\nu$) Then if 
        $\Gamma_{\mu\mu} \neq \Gamma_{\nu\nu}$ , we have:
        $ R_{\mu\nu}=R_{\nu\mu} = 0 $.
        On the other hand, if $R_{\mu\nu}\neq 0$, then
        $\Gamma_{\mu\mu}=\Gamma_{\nu\nu}$.
        This is obviously from:
        \begin{align*}
            R^{i}_{j}\Gamma^{j}_{k}=\Gamma^{i}_{j} R^{j}_k
            \Longrightarrow
            R^i_k\Gamma^k_k = \Gamma^i_i R^i_k
        \end{align*}
        where the first is automatically summed, and the second is not.

@@

        Let $A$ be a linear operator represented by matrix $A^i_j$. Let
        its adjoint $A^\dagger$ be represented by $R^i_J$. Then using
        $\braket{A^\dagger e_j, e_i} = \braket{e_j,A e_i}$, we will
        get $(R^{k}_j)^* \Omega_{ki}= \Omega_{jk}A^k_i$, i.e.
        $(R^T)^* \Omega = \Omega A$, so:
        \begin{align}
            R^\dagger = \Omega^{-1} A^\dagger \Omega
        \end{align}
        where we have used the fact that $\Omega^\dagger=\Omega$.

@@

\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    %\bibitem{book} 
    \bibitem{book_1} Zhongqi Ma, Group Theory in Physics
    \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

After mentioning the Poinc\'{a}re group, he produces to review some
concepts about linear algebra:
\begin{enumerate}
    \item The axioms of linear space, using quantum mechanics
        as basic example (Omitted).
    \item Some common concepts of linear space: linear-independence,
        subspace, direct sum, linear operators, its matrix representation. (Omitted)
    \item Introducing the complete antisymmetric tensor 
        $\epsilon^{a_1,\cdots,a_n}$. Some properties:
        \begin{align}
            \frac{1}{(m-n)!} \sum_{a_{n+1},\cdots, a_m}
            & \epsilon_{a_1,\cdots,a_n,a_{n+1},a_m}
            \epsilon_{b_1,\cdots,b_n,a_{n+1},a_m}\nonumber
            \\
            &= \sum_{p_1,\cdots,p_n} 
            \epsilon_{p_1,\cdots,p_n} 
                \delta_{a_1,b_{p_1}}\cdots \delta_{a_n,b_{p_n}}
                \\
            \epsilon_{ab}\epsilon_{rs} &=
                \delta_{ar}\delta_{bs}-\delta_{as}\delta_{br}
                \\
            \sum_d\epsilon_{abd}\epsilon_{rsd} &=
                \delta_{ar}\delta_{bs} + \delta_{as}\delta_{br}
        \end{align}
    \item Some special matrices.
    \item Fact: If $R\Gamma = \Gamma R$, and 
        $\Gamma$ is diagonal. (let $\mu\neq\nu$) Then if 
        $\Gamma_{\mu\mu} \neq \Gamma_{\nu\nu}$ , we have:
        $ R_{\mu\nu}=R_{\nu\mu} = 0 $.
        On the other hand, if $R_{\mu\nu}\neq 0$, then
        $\Gamma_{\mu\mu}=\Gamma_{\nu\nu}$.
        This is obviously from:
        \begin{align*}
            \sum_j R^{i}_{j}\Gamma^{j}_{k}=\sum_j\Gamma^{i}_{j} R^{j}_k
            \Longrightarrow
            R^i_k\Gamma^k_k = \Gamma^i_i R^i_k
        \end{align*}
        where the first is automatically summed, and the second is not.

@@

        Let $A$ be a linear operator represented by matrix $A^i_j$. Let
        its adjoint $A^\dagger$ be represented by $R^i_J$. Then using
        $\braket{A^\dagger e_j, e_i} = \braket{e_j,A e_i}$, we will
        get $(R^{k}_j)^* \Omega_{ki}= \Omega_{jk}A^k_i$, i.e.
        $(R^T)^* \Omega = \Omega A$, so:
        \begin{align}
            R = \Omega^{-1} A^\dagger \Omega
        \end{align}
        where we have used the fact that $\Omega^\dagger=\Omega$.

@@

\section{20160926}
\label{sec:20160926}

He first introduces some important matrices:

\paragraph{Unitary matrix} Eigenvalues of Unitary matrices has modulus $1$,
i.e. $|\lambda|=1$. This can be proved directly. Also, Unitary matrices are unitarily diagonalizable. This is a result of the following Spectral Theorem:
\begin{thm}[Spectral Theorem]
    A matrix $A$, which is normal (i.e. $A^\dagger A= AA^\dagger$), if and only if it is unitarily diagonalizable.
\end{thm}
\begin{proof}
    If $A$ is normal, then by Schur decomposition, we can write
    $A=UTU^\dagger$, here $U$ is unitary and $T$ is upper-triangular. 
    Using the condition of being normal, one can show directly that $T$ 
    is in fact also normal. Now we show that any triangular matrix that 
    is normal must be diagonal. Observe that we have 
    $\braket{e_i,T^\dagger T e_i}=\braket{e_i,TT^\dagger e_i}$, 
    i.e. $\braket{T^\dagger e_i, T^\dagger e_i}=\braket{T e_i, T e_i}$. 
    This is sayin g that the norm of the first column of $A^\dagger$ 
    is equal to the norm of the first column of $A$. Obviously 
    $A$ has to be diagonal.

    The converse is obvious.
\end{proof}

Also, unitary matrix's eigenvector corresponding to different eigenvalues 
are orthogonal. This is a direct result of fact mentioned above.

\paragraph{Hermitian matrices} They have real eigenvalues and orthogonal
eigenvectors (proof omitted). Also, if $\text{det}(R^\dagger R)\neq 0$,
then $R^\dagger R >0$, i.e. it is positive-definite.

\textbf{This is wong:} An example is that
the matrix $\Omega$ introduced in the previous lecture has
$\text{det}(\Omega^\dagger \Omega)=\text{det}(\Omega)$, hence
$\text{det}(\Omega)=1$ (it cannot be $0$), hence it is positive definite.

\textbf{Actually} 
$\text{det}(\Omega^\dagger \Omega)\neq\text{det}(\Omega)$, because
\begin{align}
    \sum_\rho \ket{e_\rho}\bra{e_\rho} \neq 1 \text{(unless the basis is
        orthonormal)}
    % TODO think about this in depth
\end{align}
Therefore we need anthoer argument for $\Omega$ being positive-definite.
It is provided in page 11 of \cite{book}.

\paragraph{Orthogonal matrix} For an orthogonal matrix over $\mathbb{C}$,
it is quite troublesome. For example, if $Ra=\lambda a$ and
$\lambda \neq \pm 1$, then we have $a^T a=0$, which is quite bad because
this force $a$ to have complex components.

\paragraph{Orthogonal matrix over $\mathbb{R}$} In this case, we have
similar result. But it is easy to show that for an orthogonal matrix
$R$ having only real elements, then its eigenvalues $\lambda= \pm 1$.

Then he proceeds to direct product.
\paragraph{Direct product} and also the Kronecker Product of two
matrices. Properties (let $T=R\otimes S$):
\begin{enumerate}
    \item $\mathrm{dim}T = \mathrm{dim}R \times \mathrm{dim}S$
    \item $\mathrm{tr}(T)=\mathrm{tr}(R)\mathrm{tr}(S)$
    \item $\otimes$ commutes with the operation of inverse, transpose,
        and transpose conjugation.
    \item \begin{align}
            \frac{d}{d\alpha} (R(\alpha)\otimes S(\alpha)) =
            R'(\alpha)\otimes S(\alpha) + R(\alpha)\otimes S'(\alpha)
    \end{align}
    \item when the dimentions are the same:
        \begin{enumerate}
            \item 
            $(R_1\otimes S_1)(R_2\otimes S_2) = (R_1R_2)\otimes (S_1S_2)$
        \end{enumerate}
\end{enumerate}

Finally we arrived in the group theory.
\paragraph{Symmetry examples} Dipole transition. 
$\braket{\phi_f|\hat{P}|\phi_i}$, must happen when the parity of $\phi_i$
and $\phi_f$ is of opposite parity. (pp.18 of \cite{book})

\paragraph{Group}
\begin{defi}[Group]
\nomenclature{Group}{\nomrefpage.}
    Omitted.
\end{defi}
Some basic properties (Omitted).
\begin{defi}[Abel Group]
\nomenclature{Abel Group}{\nomrefpage.}
    Omitted.
\end{defi}
\begin{defi}[Cardinality of group $\# A$]
\nomenclature{Cardinality of group $#$}{\nomrefpage.}
    Omitted.
\end{defi}

\paragraph{Multiplication table}

Facts: group of order $1,2,$ and $3$ are unique up to an isomorphism.

\begin{defi}[Cyclic group, generators]
\nomenclature{Cyclic group, generators}{\nomrefpage.}
    Omitted.
\end{defi}

\begin{defi}[$C_N,\bar{C}_N$]
\nomenclature{$C_N,\bar{C}_N$}{\nomrefpage.}
    $\bar{C}_N=C_N*\sigma$
\end{defi}
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    %\bibitem{book} 
    \bibitem{book} Zhongqi Ma, Group Theory in Physics
    \bibitem{math.se_1_lenz_vector} \href{physics.stackexchange.com/questions/18088/what-symmetry-causes-the-runge-lenz-vector-to-be-conserved}{What symmetry causes the Runge-Lenz vector to be conserved?}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
